The Functional Therapeutic Chemical Classification System

### 2013-08-20 document.tex
polish figure 3
Signed-off-by: loopasam <samuel.croset@gmail.com>

\subsection{Exploration}
The FTC was designed to assist drug repurposing analyses by explicitly representing the poly-pharmacology of 
approved drugs. In this section we exemplify how the resource can be used to perform different types of analysis.

\subsubsection{Polypharmacology spectrum}
With more information on a drug’s molecular targets and their physiological roles, the more opportunities 
exist to re-orient a drug into doing something new. The therapeutic agents described in the FTC can have several MoAs, 
representing the intrinsic polypharmacology of the approved compounds. Figure 2 illustrates the poly-pharmacology 
spectrum by showing the distribution of number of MoAs per compound. This number ranges from one to more 
than eighty for certain drugs, when indirect parents are considered. Not all the MoAs are biologically relevant, 
some FTC categories are particularly abstract (e.g, Anti-biological process agent) yet they represent discrete 
categories to which the drug belongs with an explicit and clear meaning. These discrete MoAs are a good starting 
point to understand what a compound can do when administered in a human system. The human readable definitions 
associated to each FTC category furthermore help the user to choose the adequate MoA for the desired outcome.

\begin{figure*}[!tpb]%figure3
\centerline{\includegraphics{fig3.png}}
\caption{Distribution of the direct and indirect number of MoAs per drug. 
Means are indicated with a solid line. When considering indirect categories, the distribution range is wider.}\label{fig:03}
\end{figure*}

>>>>

\subsection{Exploration}
The FTC was designed to assist drug repurposing analyses by explicitly representing the polypharmacology of 
approved drugs. In this section we exemplify how the resource can be used to perform different types of analysis.

\subsubsection{Polypharmacology spectrum}
With more information on a drug’s molecular targets and their physiological roles, the more opportunities 
exist to re-orient a drug into doing something new. The therapeutic agents described in the FTC can have several MoAs, 
representing the intrinsic polypharmacology of the approved compounds. Figure \ref{fig:03} illustrates the polypharmacology 
spectrum by showing the distribution of number of MoAs per compound. When only direct categories are considered, compounds belong on average
to 13.5 MoA categories. This number increases to 61.2 when parent categories are taken into consideration (super classes).
Not all the MoAs are disease relevant, 
some FTC categories are particularly abstract (e.g, \emph{Anti-biological process agent}) yet they represent discrete 
categories to which the drug belongs with an explicit and clear meaning. These discrete MoAs are a good starting 
point to understand what a compound can do when administered in a human system, as it will be shown with Alzheimer's disease.
The human readable definitions 
associated to each FTC category furthermore help the user to choose the adequate MoA for the desired outcome.
According to these results, compound's polypharmacology is 
well represented in the FTC, as shown by the numerous MoAs each approuved drug can exhibit.

\begin{figure*}[!tpb]%figure3
\centerline{\includegraphics{fig3.png}}
\caption{Distribution of the direct (blue) and indirect (red) number of MoAs per drug.
Means are indicated with a solid line. On average each compound has 13.5 MoAs when only direct classes are considered. The number rises
to 61.2 when indirect MoAs are included. Indirect MoAs are the ancestor classes in the taxonomy as shown in Figure \ref{fig:02}.
The ditribution range is wider (number) when indirect MoAs are considered, emphasizing the fact that some drugs
are well characterised in databases and could be used for a variety of specific biological tasks. Finally some compounds have been assigned
to a small number of FTC categories; in such cases little is known or reported about their pharmacology and repurposing opportunities
might be limited.}\label{fig:03}
\end{figure*}
